A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-06-06 discussion.tex
wording

\todo{recap the italicized stuff from above}
\vspace*{1em}
\fbox{\parbox{0.9\textwidth}{We summarize learnings from our bug patterns as follows:
\begin{itemize}
\item Being performance-awareness would be advantageous for program repair tools.
\item Understanding the effects of attributes can guide program repair.
\item Tools for inferring Rust immutability could be viable.
\end{itemize}
}}

>>>>

\vspace*{1em}
\fbox{\parbox{0.9\textwidth}{We summarize learnings from our bug patterns as follows:
\begin{itemize}
\item Rust program repair tools must understand the effects of attributes.
\item Program repair tools should be performance-aware.
\item Tools for inferring Rust immutability could be viable.
\end{itemize}
}}
